Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
fix whitespace
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
add fig
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
describe prop delay graph
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\usepackage{fullpage}
\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

\usepackage{graphicx}
\usepackage[small]{caption}
\usepackage{pstricks}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System Built on Ceph},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

\paragraph{}

@@

>>>>

\usepackage{fullpage}
\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\usepackage{graphicx}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{pstricks}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System Built on Ceph},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

@@

In Section~\ref{} we described an interface management service that is
responsible for the durable and consistent cluster-wide distribution of
interface versions. We evaluate the costs of such a service by embedding
interface definitions in a Ceph cluster membership data structure that is
managed by a Paxos instance, and distributed using a scalable, peer-to-peer
gossip protocol. We assume an architecture that consists of a light-weight
interface that enforces the semantics of interface management resulting in one
or more interface updates that must be consistent across the cluster. The
following experiments focus on the cost of achieving distribution of consistent
a interface version.

\begin{figure}[h]
\centering
\includegraphics{figures/iface-update-delay.pdf}
\caption{Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit. Each of the 120 OSDs used a RAM-based object store, while the
3 OSDs used an HDD-backed object store.}
\label{fig:propdelay}
\end{figure}

Figure~\ref{fig:propdelay} shows the CDF of the latency of distributing and
installing an interface update on all OSDs in the cluster. The latency is
defined as the elapsed time following the Paxos proposal for an interface
update until each OSDs makes the update live (he cost of the Paxos proposal is
configurable and is discussed below). The latency measurements were taken on
the nodes running Ceph server daemons (the Paxos servers and OSDs nodes), and
thus excludes the client round-trip cost. In each of the experiments 1000
interface updates were observed.

The first experiment shown in Figure~\ref{fig:propdelay} illustrates a lower
bound cost for updates in a large cluster by avoiding disk I/O for storing
interface updates locally within each OSD.  In the experiment labeled "120 OSD
(RAM)" a cluster of 120 OSDs (10 OSDs x 12 servers) using an in-memory data
store were deployed, showing a latency of less than 54 ms with a probability of
90\% and a worst case latency of 194 ms. The curve labeled "3 OSD (HDD)" is a
smaller cluster where each of the three OSDs uses a spinning disk as the object
store that saves a copy of the cluster map ({\bf is this I/O before its made
live?}), and shows a latency of 37 ms with a 90\% probability and a worst case
latency of 255 ms. Since the cost of a disk I/O is larger than the same I/O
executed against the in-memory device, the predominant cost in a lightly loaded
cluster appears to be the number of OSDs.

The real cost of interface management, in addition to cluster-wide propagation
of interface updates, includes the network round-trip to the interface
management service, the Paxos commit protocol, and other factors such as system
load. By default Paxos proposals occur periodically with a 1 second interval in
order to accumulate updates. In a minimum realistic quorum of 3 monitors using
HDD-based storage, we were able to decrease this interval to an average of 222
ms.
